Enhancement of SDR in Thessaloniki Clear Sky

### 2024-05-13 GHI_enh_03_process.tex
Commit 2024-05-13 12:21

  \usepackage{unicode-math} % this also loads fontspec

@@

\ifPDFTeX\else
  % xetex/luatex font selection

@@

@@

\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}

@@

\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}

@@

\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}

@@

\urlstyle{same}

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-09}

@@

\begin{verbatim}

Call:
stats::lm(formula = .formula, data = df)

@@

\begin{verbatim}

Call:
lm(formula = ST_E_monthly$wattGLB.N ~ ST_E_monthly$Date)

@@

\begin{verbatim}
2024-05-09 20:10:12.1 athan@sagan GHI_enh_03_process.R 3.712139 mins
\end{verbatim}

>>>>

  \usepackage{unicode-math}

@@

@@

\urlstyle{same} % disable monospaced font for URLs

@@

\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}

@@

\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}

@@

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-13}

@@

\begin{verbatim}
Call:
stats::lm(formula = .formula, data = df)

@@

\begin{verbatim}
Call:
lm(formula = ST_E_monthly$wattGLB.N ~ ST_E_monthly$Date)

@@

\begin{verbatim}
2024-05-13 09:11:34.5 athan@sagan GHI_enh_03_process.R 3.715344 mins
\end{verbatim}

### 2024-05-13 GHI_enh_CSid.tex
Commit 2024-05-13 12:21

\title{Enhancement of SDR in Thessaloniki Clear Sky}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-09}

@@

\DocumentationTok{\#\# for trend mean}
\CommentTok{\# trend\_apply  \textless{}{-} trend\_mean}
\CommentTok{\# trend\_factor \textless{}{-} {-}0.01995656}
\DocumentationTok{\#\# for trend median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}

\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply}\NormalTok{(tsy) }\SpecialCharTok{+}\NormalTok{ trend\_factor)]}

@@

  \CommentTok{\# DATA[, sum( abs((Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x)) {-} wattGLB)) ]}

  \CommentTok{\# DATA[, sum(1 {-} (Enhanc\_C\_4\_ref * (1 + trend\_apply(tsy) * x) / wattGLB)) ]}

@@

@@

\NormalTok{DTyear }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                   \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
                   \AttributeTok{Ref =} \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref),}
                   \AttributeTok{Thr =} \FunctionTok{mean}\NormalTok{(Thresh\_test),}
\NormalTok{                   .N),}
\NormalTok{               by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date))]}

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-6-5} \end{center}

@@

\begin{verbatim}
$mae
[1] 83.65625

$mse
[1] 7337.38

$rmse
[1] 85.65851

$mape
[1] 0.1442124

$nmse
[1] 34.56461

$rstd
[1] 0.1471491
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_CSid_files/figure-latex/unnamed-chunk-7-5} \end{center}

>>>>

\title{Enhancement of SDR in Thessaloniki Clear Sky}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-05-13}

@@

\DocumentationTok{\#\# for trend mean}
\CommentTok{\# trend\_apply  \textless{}{-} trend\_mean}
\CommentTok{\# trend\_factor \textless{}{-} {-}0.01995656}
\DocumentationTok{\#\# for trend median}
\NormalTok{trend\_apply  }\OtherTok{\textless{}{-}}\NormalTok{ trend\_median}
\NormalTok{trend\_factor }\OtherTok{\textless{}{-}} \SpecialCharTok{{-}}\FloatTok{0.01995656}  \CommentTok{\# the same}
\NormalTok{trend\_apply\_adj }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(tsy) \{}
  \FunctionTok{trend\_median}\NormalTok{(tsy) }\SpecialCharTok{{-}} \FloatTok{0.01995656}
\NormalTok{\}}

\FunctionTok{trend\_apply}\NormalTok{(}\DecValTok{1999}\SpecialCharTok{:}\DecValTok{2000}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
[1] -0.01599489 -0.01332907
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{DATA[, Thresh\_test }\SpecialCharTok{:=}\NormalTok{ Enhanc\_C\_4\_ref }\SpecialCharTok{*}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{trend\_apply\_adj}\NormalTok{(tsy))]}

@@

@@

\NormalTok{DTdaily }\OtherTok{\textless{}{-}}\NormalTok{ DATA[,}
\NormalTok{                .(}
                  \AttributeTok{glo\_Sum    =} \FunctionTok{sum}\NormalTok{(Low\_B.Low\_W.glo),}
                  \AttributeTok{GLB\_Sum    =} \FunctionTok{sum}\NormalTok{(wattGLB),}
                  \AttributeTok{GLB\_N      =} \FunctionTok{sum}\NormalTok{(}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(wattGLB)),}
                  \AttributeTok{DayLength  =} \FunctionTok{max}\NormalTok{(DayLength),}
                  \AttributeTok{En\_Ref\_sum =} \FunctionTok{sum}\NormalTok{(Enhanc\_C\_4\_ref),}
                  \CommentTok{\# Thresh\_sum = sum(Thresh\_test),}
\NormalTok{                  .N}
\NormalTok{                ),}
\NormalTok{                by }\OtherTok{=}\NormalTok{ Day]}

@@

\NormalTok{DTyear }\OtherTok{\textless{}{-}}\NormalTok{ DATA[, .(}\AttributeTok{glo =} \FunctionTok{mean}\NormalTok{(Low\_B.Low\_W.glo),}
                   \AttributeTok{GLB =} \FunctionTok{mean}\NormalTok{(wattGLB),}
                   \AttributeTok{Ref =} \FunctionTok{mean}\NormalTok{(Enhanc\_C\_4\_ref),}
                   \CommentTok{\# Thr = mean(Thresh\_test),}
\NormalTok{                   .N),}
\NormalTok{               by }\OtherTok{=}\NormalTok{ .(}\FunctionTok{year}\NormalTok{(Date))]}

@@

\newpage

@@

\newpage

@@
